---
title: "Semantic Networks Analysis"
author: "Abhilasha Kumar"
date: "January 16, 2018"
output:
  pdf_document: default
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading the Data

``` {r warning=F, message=F}
library(dplyr)
sem = read.csv("NetworksProject_AllSubjects.csv", header = TRUE, sep = ",")
sem$mean_len = as.double(as.character(sem$mean_len))
sem$mean_logf = as.double(as.character(sem$mean_logf))
sem$mean_ldtz = as.double(as.character(sem$mean_ldtz))
sem$mean_nmgz = as.double(as.character(sem$mean_nmgz))
sem$undirected = as.double(as.character(sem$undirected))
sem$directed = as.double(as.character(sem$directed))
sem$logp = as.double(as.character(sem$logp))

sem$mean_len = round(sem$mean_len, 2)
sem$mean_logf = round(sem$mean_logf, 2)
sem$mean_ldtz = round(sem$mean_ldtz, 2)
sem$mean_nmgz = round(sem$mean_nmgz, 2)

itemlist = read.csv("KenettCompleteItemList.csv", header = TRUE, sep = ",")
colnames(itemlist) = c("prime_word", "target_word", "ItemNo", "List", "proc")
itemlist$prime_word = paste(itemlist$prime_word, "")
itemlist$target_word = paste(itemlist$target_word, "")
sem$prime_word = as.character(sem$prime_word)
sem$target_word = as.character(sem$target_word)
sem$proc = as.character(sem$proc)
itemlist$proc = as.character(itemlist$proc)

## Problem in ITEM NAIVE-INTEREST due to coding issues 
## So we replae this item by simple text

sem$prime_word = ifelse(sem$prime_word == "NAÃ\u008fVE ", "NA\xecVE ", 
                        sem$prime_word)
sem$target_word = ifelse(sem$target_word == "NAÃ\u008fVE ", "NA\xecVE ", 
                        sem$target_word)

sem = inner_join(sem, itemlist, by = c("prime_word", 
                                          "target_word", "proc"))

sem = sem[order(sem$subject),]

kenettproc= group_by(sem, ItemNo) %>%
  summarise(items = n())

```
# Related-Unrelated Decisions
``` {r  warning=F, message=F}
library(dplyr)

sem_decision = group_by(sem, subject, pathlength, Type ) %>%
  summarize(Trials = n())

sem_subjectrows  = group_by(sem_decision, subject) %>%
  summarise(numrows = n())
rows = which(sem_subjectrows$numrows < 12)

subjects = sem_subjectrows[rows,]

# With N = 80, there are 12 rowas missing!

sem_decision[949,] = c("42406", 15, "Related", 0)
sem_decision[950,] = c("61558", 15, "Related", 0)
sem_decision[951,] = c("27113", 15, "Related", 0)
sem_decision[952,] = c("34686", 6, "Related", 0)
sem_decision[953,] = c("81385", 6, "Related", 0)
sem_decision[954,] = c("35312", 3, "Related", 0)
sem_decision[955,] = c("65089", 1, "Unrelated", 0)
sem_decision[956,] = c("65448", 4, "Related", 0)
sem_decision[957,] = c("65448", 15, "Related", 0)
sem_decision[958,] = c("84694", 6, "Related", 0)

sem_decision[959,] = c("7416", 15, "Related", 0)
sem_decision[960,] = c("79426", 15, "Related", 0)



sem_decision$Trials = as.numeric(as.character(sem_decision$Trials))

sem_decision_agg = group_by(sem_decision, pathlength, Type ) %>%
  summarise_at(vars(Trials), mean)
```


### Plotting Proportions

``` {r warning=F, message=F, fig.align='center'}
sem_decision$Trials = as.numeric(as.character(sem_decision$Trials))
sem_decision_agg$Trials = as.numeric(as.character(sem_decision_agg$Trials))

sem_decision$proportion = sem_decision$Trials/40


sem_decision_agg$proportion = sem_decision_agg$Trials/(40)

sem_decision$pathlengthfac = ordered(as.factor(as.character(sem_decision$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))

sem_decision_agg$pathlengthfac = ordered(as.factor(as.character(sem_decision_agg$pathlength)), 
                            levels = c("1", "2", "3", "4", "6","15"))

library(ggplot2)
library(ggthemes)

sem_decision_agg = sem_decision_agg[order(sem_decision_agg$pathlength,
                                          sem_decision_agg$Type),]

sem_decision_agg %>% mutate(WordPair = factor(Type, 
                                        levels = unique(Type),
                    labels = c("Related", "Unrelated")))%>%
  ggplot(aes(x = pathlengthfac, y = proportion, 
                              fill = WordPair, group = WordPair))+
 geom_bar(stat = "identity", position = "dodge", width = 0.7, color= "black")+
 #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
 scale_fill_solarized()+
    xlab("Path Length") + ylab("Proportion of Trials") + 
  ggtitle("Subject-Level Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Line Plot Subject-Wise

``` {r warning=F, message=F}
sem_decision$subject = as.factor(as.character(sem_decision$subject))


sem_decision = sem_decision[order(sem_decision$subject, 
                                  sem_decision$pathlength, 
                                  sem_decision$Type),]

sem_decision %>% mutate(WordPair = factor(Type, 
                                        levels = unique(Type),
                    labels = c("Related", "Unrelated")))%>%
  ggplot(aes(x = pathlengthfac, y = proportion,
             color = WordPair, group=interaction(WordPair, subject))) + 
  geom_point()+
 geom_line() + 
 theme_few()+
 scale_fill_solarized()+
 # facet_wrap(~subject)+
    xlab("Path Length") + ylab("Proportion of Trials") + 
  ggtitle("Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### ANOVA

```{r}
relunrel_aov = aov(data = sem_decision, proportion ~ pathlengthfac*Type + 
                     Error(subject/(pathlengthfac*Type)))
summary(relunrel_aov)

options(contrasts = c('contr.sum', 'contr.poly'))
 library(lsmeans)
 library(multcomp)
 sem_lsm = lsmeans::lsmeans(relunrel_aov, c("pathlengthfac", "Type"))
 prime_effect = cld(sem_lsm, alpha = 0.05, 
                 adjust = "tukey", details = TRUE, by = "pathlengthfac")
 library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.05))
```


#Raw Reaction Time

```{r}
sem_rt = group_by(sem, subject, pathlength ) %>%
  summarise_at(vars(rt), mean)

sem_rt_agg = group_by(sem, pathlength ) %>%
  summarise_at(vars(rt), mean)

sem_agg_rmisc = Rmisc::summarySE(sem_rt, 
                        measurevar = "rt",
                        groupvars = c("pathlength"))
```

### ANOVA

```{r}
sem_rt$pathlengthfac = ordered(as.factor(as.character(sem_rt$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
sem_rt$subject = as.factor(sem_rt$subject)
rt_aov = aov(data = sem_rt, rt ~ pathlengthfac + 
                     Error(subject/(pathlengthfac)))
summary(rt_aov)
```

### Plotting RTs

``` {r  }

sem_agg_rmisc$pathlengthfac = ordered(as.factor(as.character(sem_agg_rmisc$pathlength)),                             levels = c("1", "2", "3", "4",  "6", "15"))

library(ggplot2)
library(ggthemes)

sem_agg_rmisc %>% 
  ggplot(aes(x = pathlengthfac, y = rt, group = 1))+
  geom_point()+
  geom_line(color = "red")+
   geom_errorbar(aes(ymin=rt - ci, ymax=rt + ci), 
             width=.2, color = "gray26", 
             position = position_dodge(0.7))+
 theme_few()+
 # scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Subject-Wise

``` {r  }

library(ggplot2)
library(ggthemes)

sem_rt %>% 
  ggplot(aes(x = pathlengthfac, y = rt, 
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  guides(color = FALSE)+
 # scale_x_continuous(breaks = c(1,2,3,4,6,15))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_blank(),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

# z-scored Reaction Time

## First Trim

``` {r  }
library(dplyr)
sem_firsttrim = sem %>% filter( rt > 250 & rt < 2000)
```

## Raw RT aggregates After Trimming

``` {r  }
sem_rt_firsttrim = group_by(sem_firsttrim, subject, pathlength ) %>%
  summarise_at(vars(rt), mean)

sem_rt_agg_firsttrim = group_by(sem_firsttrim, pathlength ) %>%
  summarise_at(vars(rt), mean)

sem_rt_agg_firsttrim$pathlengthfac = ordered(as.factor(as.character(sem_rt_agg_firsttrim$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

library(ggplot2)
library(ggthemes)

sem_rt_agg_firsttrim %>% 
  ggplot(aes(x = pathlengthfac, y = rt, group = 1))+
  geom_point()+
  geom_line(color = "red")+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,6,15))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```


## Making the z-scores
``` {r  }
## aggregate per subject all IVs and DVs
meanRT = group_by(sem_firsttrim, subject) %>%
  summarise_at(vars(rt), mean)
colnames(meanRT) = c("subject", "MeanRT")

sdRT = group_by(sem_firsttrim, subject) %>%
  summarise_at(vars(rt), sd)
colnames(sdRT) = c("subject", "sdRT")

RT_agg = merge(meanRT, sdRT, by = "subject")

## merge aggregate info with long data
sem_z = merge(sem_firsttrim, RT_agg, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
sem_z = sem_z %>% mutate(zRT = (rt - MeanRT)/sdRT)
                 
## checking: subject level means should be zero

sub_pic = group_by(sem_z, subject) %>%
  summarise_at(vars(zRT), mean)

```


## Trimming z-RT

``` {r  }
sem_z_trimmed = subset(sem_z, sem_z$zRT < 3 & sem_z$zRT > -3)
```

## Repeating z-scoring

``` {r  }
library(dplyr)

## aggregate per subject all IVs and DVs
meanRT_trim = group_by(sem_z_trimmed, subject) %>%
  summarise_at(vars(rt), mean)
colnames(meanRT_trim) = c("subject", "MeanRT_trim")

sdRT_trim = group_by(sem_z_trimmed, subject) %>%
  summarise_at(vars(rt), sd)
colnames(sdRT_trim) = c("subject", "sdRT_trim")

RT_agg_trim = merge(meanRT_trim, sdRT_trim, by = "subject")

## merge aggregate info with long data
new_sem_z = merge(sem_z_trimmed, RT_agg_trim, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
new_sem_z = new_sem_z %>% mutate(zRT_trim = (rt - MeanRT_trim)/sdRT_trim)
                 
## checking: subject level means should be zero

sub_pic = group_by(new_sem_z, subject) %>%
  summarise_at(vars(zRT_trim), mean)

#write.csv(new_pic_z, file="final_pic_z.csv")
```

## Aggregating zRT
``` {r}
z_sem_rt = group_by(new_sem_z, subject, pathlength ) %>%
  summarise_at(vars(zRT_trim, rt), mean)

z_sem_rt_rel = group_by(new_sem_z, subject, pathlength, Type ) %>%
  summarise_at(vars(zRT_trim, rt), mean)

z_sem_rt_agg = group_by(new_sem_z, pathlength ) %>%
  summarise_at(vars(zRT_trim), mean)

z_rmisc = Rmisc::summarySE(new_sem_z, 
                        measurevar = "zRT_trim",
                        groupvars = c("pathlength"))

z_sem_rt_rel_agg = group_by(new_sem_z, pathlength, Type ) %>%
  summarise_at(vars(zRT_trim), mean)

z_sem_rt_rel_agg_rmisc = Rmisc::summarySE(new_sem_z, 
                        measurevar = "zRT_trim",
                        groupvars = c("pathlength", "Type"))
```

## ANOVA
```{r}
z_sem_rt$pathlengthfac = ordered(as.factor(as.character(z_sem_rt$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
z_sem_rt$subject = as.factor(z_sem_rt$subject)

z_rt_aov = aov(data = z_sem_rt, zRT_trim ~ pathlengthfac + 
                     Error(subject/(pathlengthfac)))
summary(z_rt_aov)

options(contrasts = c('contr.sum', 'contr.poly'))
 library(lsmeans)
 library(multcomp)
 sem_lsm = lsmeans::lsmeans(z_rt_aov, c("pathlengthfac"))
 prime_effect = cld(sem_lsm, alpha = 0.05, 
                 adjust = "tukey", details = TRUE)
 library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.1 ))

```

## Plotting RTs: Rel-Unrel 

``` {r  }

z_sem_rt_rel_agg_rmisc$pathlengthfac = ordered(as.factor(as.character(z_sem_rt_rel_agg_rmisc$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

z_sem_rt_rel_agg_rmisc$zRT_trim = as.numeric(z_sem_rt_rel_agg_rmisc$zRT_trim)

library(ggplot2)
library(ggthemes)

z_sem_rt_rel_agg_rmisc %>% 
  ggplot(aes(x = pathlengthfac, y = zRT_trim, group = Type, color = Type))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line()+
  geom_errorbar(aes(ymin=zRT_trim - ci, ymax=zRT_trim + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0.05))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT") + 
  ggtitle("z-RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Quadratic Trend

```{r}
z_sem_rt %>% 
  ggplot(aes(x = pathlength, y = zRT_trim))+
  geom_point(color = "black", size = 1)+
  geom_smooth(method = "loess", color = "red")+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
 # scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT") + 
  ggtitle("z-RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

# Regressions
``` {r  }
library(lme4)
sem$pathlengthfac = ordered(as.factor(as.character(sem$pathlength)), 
                            levels = c("1", "2", "3", "4", "6","15"))

new_sem_z$pathlengthfac = ordered(as.factor(as.character(new_sem_z$pathlength)), 
                            levels = c("1", "2", "3", "4", "6","15"))
 
m0 = lmer(data = new_sem_z, rt ~ 1 + (1|subject) + (1|trial_index) +
            (1|ItemNo))
summary(m0)
reghelper::ICC(m0)

contrasts(sem$pathlengthfac) = contr.treatment(6, base = 1)


contrasts(new_sem_z$pathlengthfac) = contr.treatment(6, base = 2)

m1_fixed = lmer(data = new_sem_z, zRT_trim ~ pathlengthfac +
           (1|subject) + (1|ItemNo) + (1|trial_index))
summary(m1_fixed)
```

# Concreteness Norms

```{r}
elpnorms = read.csv("ELP_norms.csv", header = TRUE, sep = ",")
elpnorms = elpnorms[,c(1,2)]
colnames(elpnorms) = c("prime_word", "prime_concreteness")
elpnorms$prime_word = toupper(elpnorms$prime_word)
elpnorms$prime_word = paste(elpnorms$prime_word, "")

elpnorms$prime_word = as.character(elpnorms$prime_word)

sem$prime_word = as.character(sem$prime_word)
merged_sem_prime= inner_join(sem, elpnorms, by = "prime_word")
merged_sem_prime = merged_sem_prime[,c(4,7,16,41)]

colnames(elpnorms) = c("target_word", "target_concreteness")
sem$target_word = as.character(sem$target_word)
merged_sem_target= inner_join(sem, elpnorms, by = "target_word")
merged_sem_target = merged_sem_target[,c(4,7, 17,41)]

merged_concretness = full_join(merged_sem_prime, merged_sem_target,
                           by = c("trial_index", "subject"))
merged_concretness$mean_conc = (merged_concretness$prime_concreteness +
                                merged_concretness$target_concreteness) / 2

### NOW WE HAVE CONCRETENESS NORMS FOR ALL ITEMS IN THE DATASET
### NEED TO COMBINE THIS WITH ACTUAL SEM DATA

new_sem_z$prime_word = as.character(new_sem_z$prime_word)
new_sem_z$target_word = as.character(new_sem_z$target_word)
final_sem = inner_join(new_sem_z, merged_concretness, 
                      by = c("trial_index", "subject", 
                             "prime_word", "target_word") )

```

### Conreteness Model

```{r}
final_sem$pathlengthfac = ordered(as.factor(as.character(final_sem$pathlength)), 
                            levels = c("1", "2", "3", "4", "6","15"))
 
elp_model = lmer(data = final_sem, zRT_trim ~ mean_len + mean_logf +
                   mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) + (1|ItemNo))
fit_from_elp = broom::augment(elp_model,final_sem)
 
contrasts(fit_from_elp$pathlengthfac) = contr.treatment(6, base = 2)
 
m1_fixed_elp = lmer(data = fit_from_elp, .resid ~ pathlengthfac +
           (1|subject) + (1|trial_index) + (1|ItemNo))
 summary(m1_fixed_elp)
 
 contrasts(final_sem$pathlengthfac) = contr.treatment(6, base = 2)

 m1_all_elp = lme4::lmer(data = final_sem, zRT_trim ~ pathlengthfac +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) + (1|ItemNo))
 summary(m1_all_elp)
 
 # m1_all_elp_random = lme4::lmer(data = final_sem, zRT_trim ~ pathlengthfac +
 #                     mean_len + mean_logf + mean_ldtz + mean_conc +
 #           (pathlengthfac|subject) + 
 #              + (1|trial_index) + (pathlengthfac|ItemNo),
 #    control=lmerControl(optimizer="bobyqa",
 #            optCtrl=list(maxfun=1000000)))
 # summary(m1_all_elp_random)
 # 
 ## centering so that contrasts are easier
final_sem$mean_len_c = scale(final_sem$mean_len, 
                             center = TRUE, scale = FALSE)
final_sem$mean_logf_c = scale(final_sem$mean_logf, 
                              center = TRUE, scale = FALSE)
final_sem$mean_ldtz_c = scale(final_sem$mean_ldtz, 
                              center = TRUE, scale = FALSE)
final_sem$mean_conc_c = scale(final_sem$mean_conc, 
                              center = TRUE, scale = FALSE)

 m1_all_elp_type = lme4::lmer(data = final_sem, 
                              zRT_trim ~ pathlengthfac*Type +
                     mean_len_c + mean_logf_c + mean_ldtz_c + mean_conc_c +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
 summary(m1_all_elp_type)
 
 m1_all_elp_type_withoutcov = lme4::lmer(data = final_sem, 
                              zRT_trim ~ pathlengthfac*Type +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
 summary(m1_all_elp_type_withoutcov)
 
```

# Item Diagnostics

```{r}
item_mean = group_by(new_sem_z, pathlength, ItemNo) %>%
  summarise_at(vars(zRT_trim), mean)

item_rel = group_by(sem, pathlength, ItemNo, Type) %>%
  summarise(Trials = n())

item_rel_rt = group_by(sem, pathlength, ItemNo, Type) %>%
  summarise_at(vars(rt), mean)

item_rt_collapsed = group_by(sem, pathlength, ItemNo) %>%
  summarise_at(vars(rt), mean)

item_rel_wide = tidyr::spread(item_rel, Type, Trials)

item_rel_rt_wide = tidyr::spread(item_rel_rt, Type, rt)

item_sub = group_by(sem, ItemNo, subject) %>%
  summarise(Subjects = n())

item_rel_wide$Related  = ifelse(is.na(item_rel_wide$Related), 0, item_rel_wide$Related)

item_rel_wide$Unrelated  = ifelse(is.na(item_rel_wide$Unrelated), 0, item_rel_wide$Unrelated)

item_rel_rt_wide$Related  = ifelse(is.na(item_rel_rt_wide$Related), 0, item_rel_rt_wide$Related)

item_rel_rt_wide$Unrelated  = ifelse(is.na(item_rel_rt_wide$Unrelated), 0, item_rel_rt_wide$Unrelated)
```

# Item Level Analyses

## Proportion of Subjects

### Plot

```{r}
## we have item_rel_wide and item_rel_rt_wide with RTs and number of subjects
## who called these items related/unrelated for each path length

item_rel_main = merge(item_rel, item_rel_rt,
                      by = c("pathlength", "ItemNo", "Type"))
colnames(item_rel_main) =c ("pathlength", "ItemNo", 
                            "Type", "Trials","rt")

itemrt_agg = Rmisc::summarySE(item_rel_main, 
                        measurevar = "rt",
                        groupvars = c("pathlength", "Type"))

itemrt_agg_collapsed = Rmisc::summarySE(item_rt_collapsed, 
                        measurevar = "rt",
                        groupvars = c("pathlength"))

item_rel_main$Proportion = item_rel_main$Trials/16


item_agg = Rmisc::summarySE(item_rel_main, 
                        measurevar = "Proportion",
                        groupvars = c("pathlength", "Type"))
item_agg$pathlengthfac = ordered(as.factor(as.character(item_agg$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))

item_agg %>% 
  ggplot(aes(x = pathlengthfac, y = Proportion, group = Type, fill = Type))+
#  geom_smooth(method = "loess")+
 geom_bar(stat = "identity", position = "dodge", width = 0.7, color= "black")+
  geom_errorbar(aes(ymin=Proportion - ci, ymax=Proportion + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0.8))+
 theme_few()+
  scale_fill_solarized()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Number of Subjects") + 
  ggtitle("Item-Level Subject Counts for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### ANOVA

```{r}

## item_rel_wide has 1200 rows with 0s for items. convert that into wide.

library(tidyr)
item_prop_data = item_rel_wide %>%
  gather(Type, Trials, Related:Unrelated)

item_prop_data$Proportion = item_prop_data$Trials/16

item_prop_data = item_prop_data[order(item_prop_data$ItemNo),]

item_prop_data$pathlengthfac = ordered(as.factor(as.character(item_prop_data$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
library(lme4)
itemrelunrel_aov = aov(data = item_prop_data, 
                       Proportion ~ pathlengthfac*Type + 
                     Error(ItemNo/(Type)))
summary(itemrelunrel_aov)
```

## Raw RT Plot Rel-Unrel

```{r}
itemrt_agg$pathlengthfac = ordered(as.factor(as.character(itemrt_agg$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))

itemrt_agg %>% 
  ggplot(aes(x = pathlengthfac, y = rt, group = Type, color = Type))+
#  geom_smooth(method = "loess")+
  geom_point()+
geom_line()+
  geom_errorbar(aes(ymin=rt - ci, ymax=rt + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Raw RT") + 
  ggtitle("Item-Level Raw RTs for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### RT ANOVA Rel-Unrel

```{r}
item_rel_main$pathlengthfac = ordered(as.factor(as.character(item_rel_main$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
contrasts(item_rel_main$pathlengthfac) = contr.treatment(6, base = 2)
contrasts(item_rel_main$Type) = contr.treatment(2, base = 2)


item_rt_aov = lme4::lmer(data = item_rel_main, rt ~ pathlengthfac*Type +
                          (1|ItemNo))
summary(item_rt_aov)
car::Anova(item_rt_aov)
```

# Word2vec Model

```{r}
word2vec = read.csv("word2veccosines.csv", header = TRUE, sep = ",")

final_word2vec = merge(final_sem, word2vec, 
                       by = c( "ItemNo", "proc"))
final_word2vec$mean_conc_c = as.numeric(final_word2vec$mean_conc_c)
final_word2vec$mean_len_c = as.numeric(final_word2vec$mean_len_c)
final_word2vec$mean_logf_c = as.numeric(final_word2vec$mean_logf_c)
final_word2vec$mean_ldtz_c = as.numeric(final_word2vec$mean_ldtz_c)

final_word2vec = final_word2vec %>% arrange(subject, ItemNo)

m1_word2vec = lme4::lmer(data = final_word2vec, 
                              zRT_trim ~ word2veccosine*Type +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
 summary(m1_word2vec)
 m1_pathlength = lme4::lmer(data = final_word2vec, 
                              zRT_trim ~ pathlengthfac*Type +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
 summary(m1_pathlength)
 
 anova(m1_pathlength,m1_word2vec)

```

## ScatterPlot

### Kenett and Word2Vec
```{r}

item_word2vec = group_by(final_word2vec, ItemNo) %>%
  summarise_at(vars(pathlength,undirected, word2veccosine), mean)
item_word2vec$pathlengthfac = ordered(as.factor(as.character(item_word2vec$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
ggplot(item_word2vec, 
       aes(x = pathlength, y = word2veccosine))+
geom_point()+
  geom_smooth(method = "lm")+
 theme_few()+
    xlab("Path Length") + ylab("Cosine Similarity") + 
  ggtitle("Correlation between Kenett Path Length & Word2Vec Cosines")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Kenett and Word2Vec
```{r}

ggplot(item_word2vec, 
       aes(x = undirected, y = word2veccosine))+
geom_point()+
  geom_smooth(method = "lm")+
 theme_few()+
    xlab("Path Length") + ylab("Cosine Similarity") + 
  ggtitle("Correlation between Non Directed & Word2Vec Cosines")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

 