---
title: "Semantic Networks Analysis"
author: "Abhilasha Kumar"
date: "January 16, 2018"
output:
  pdf_document: default
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading the Data

```{r, echo=FALSE}
sem = read.csv("NetworksProject_AllSubjects.csv", header = TRUE, sep = ",")
sem$mean_len = as.double(as.character(sem$mean_len))
sem$mean_logf = as.double(as.character(sem$mean_logf))
sem$mean_ldtz = as.double(as.character(sem$mean_ldtz))
sem$mean_nmgz = as.double(as.character(sem$mean_nmgz))
sem$undirected = as.double(as.character(sem$undirected))
sem$directed = as.double(as.character(sem$directed))
sem$logp = as.double(as.character(sem$logp))

sem$mean_len = round(sem$mean_len, 2)
sem$mean_logf = round(sem$mean_logf, 2)
sem$mean_ldtz = round(sem$mean_ldtz, 2)
sem$mean_nmgz = round(sem$mean_nmgz, 2)


```
# Related-Unrelated Decisions
```{r, echo=FALSE}
library(dplyr)

sem_decision = group_by(sem, subject, pathlength, Type ) %>%
  summarize(Trials = n())

# With N = 40, there are 10 rowas missing!

sem_decision[471,] = c("42406", 15, "Related", 0)
sem_decision[472,] = c("61558", 15, "Related", 0)
sem_decision[473,] = c("27113", 15, "Related", 0)
sem_decision[474,] = c("34686", 6, "Related", 0)
sem_decision[475,] = c("81385", 6, "Related", 0)
sem_decision[476,] = c("35312", 3, "Related", 0)
sem_decision[477,] = c("65089", 1, "Unrelated", 0)
sem_decision[478,] = c("65448", 4, "Related", 0)
sem_decision[479,] = c("65448", 15, "Related", 0)
sem_decision[480,] = c("84694", 6, "Related", 0)



sem_decision$Trials = as.numeric(as.character(sem_decision$Trials))

sem_decision_agg = group_by(sem_decision, pathlength, Type ) %>%
  summarise_at(vars(Trials), mean)




```


### Plotting Proportions

```{r, echo=FALSE, fig.align='center'}
sem_decision$Trials = as.numeric(as.character(sem_decision$Trials))
sem_decision_agg$Trials = as.numeric(as.character(sem_decision_agg$Trials))

sem_decision$proportion = sem_decision$Trials/40


sem_decision_agg$proportion = sem_decision_agg$Trials/(40)

sem_decision$pathlengthfac = ordered(as.factor(as.character(sem_decision$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))

sem_decision_agg$pathlengthfac = ordered(as.factor(as.character(sem_decision_agg$pathlength)), 
                            levels = c("1", "2", "3", "4", "6","15"))

library(ggplot2)
library(ggthemes)

sem_decision_agg = sem_decision_agg[order(sem_decision_agg$pathlength,
                                          sem_decision_agg$Type),]

sem_decision_agg %>% mutate(WordPair = factor(Type, 
                                        levels = unique(Type),
                    labels = c("Related", "Unrelated")))%>%
  ggplot(aes(x = pathlengthfac, y = proportion, 
                              fill = WordPair, group = WordPair))+
 geom_bar(stat = "identity", position = "dodge", width = 0.7, color= "black")+
 #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
 scale_fill_solarized()+
    xlab("Path Length") + ylab("Proportion of Trials") + 
  ggtitle("Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```


### Subject-Wise

```{r, echo=FALSE}
sem_decision$subject = as.factor(as.character(sem_decision$subject))


sem_decision = sem_decision[order(sem_decision$subject, 
                                  sem_decision$pathlength, 
                                  sem_decision$Type),]

sem_decision %>% mutate(WordPair = factor(Type, 
                                        levels = unique(Type),
                    labels = c("Related", "Unrelated")))%>%
  ggplot(aes(x = pathlengthfac, y = proportion, 
                              fill = WordPair, group = WordPair))+
 geom_bar(stat = "identity", position = "dodge", width = 0.7, color= "black")+
 #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
 scale_fill_solarized()+
  facet_wrap(~subject)+
    xlab("Path Length") + ylab("Proportion of Trials") + 
  ggtitle("Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Line Plot Subject-Wise

```{r, echo=FALSE}
sem_decision$subject = as.factor(as.character(sem_decision$subject))


sem_decision = sem_decision[order(sem_decision$subject, 
                                  sem_decision$pathlength, 
                                  sem_decision$Type),]

sem_decision %>% mutate(WordPair = factor(Type, 
                                        levels = unique(Type),
                    labels = c("Related", "Unrelated")))%>%
  ggplot(aes(x = pathlengthfac, y = proportion,
             color = WordPair, group=interaction(WordPair, subject))) + 
  geom_point()+
 geom_line() + 
 theme_few()+
 scale_fill_solarized()+
 # facet_wrap(~subject)+
    xlab("Path Length") + ylab("Proportion of Trials") + 
  ggtitle("Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### ANOVA

```{r}
relunrel_aov = aov(data = sem_decision, proportion ~ pathlengthfac*Type + 
                     Error(subject/(pathlengthfac*Type)))
summary(relunrel_aov)
```


#Raw Reaction Time

```{r, echo=FALSE}
sem_rt = group_by(sem, subject, pathlength ) %>%
  summarise_at(vars(rt), mean)

sem_rt_agg = group_by(sem, pathlength ) %>%
  summarise_at(vars(rt), mean)

sem_agg_rmisc = Rmisc::summarySE(sem_rt, 
                        measurevar = "rt",
                        groupvars = c("pathlength"))
```

### ANOVA

```{r}
sem_rt$pathlengthfac = ordered(as.factor(as.character(sem_rt$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
sem_rt$subject = as.factor(sem_rt$subject)
rt_aov = aov(data = sem_rt, rt ~ pathlengthfac + 
                     Error(subject/(pathlengthfac)))
summary(rt_aov)
```

### Plotting RTs

```{r, echo=FALSE}

sem_agg_rmisc$pathlengthfac = ordered(as.factor(as.character(sem_agg_rmisc$pathlength)),                             levels = c("1", "2", "3", "4",  "6", "15"))

library(ggplot2)
library(ggthemes)

sem_agg_rmisc %>% 
  ggplot(aes(x = pathlengthfac, y = rt, group = 1))+
  geom_point()+
  geom_line(color = "red")+
   geom_errorbar(aes(ymin=rt - ci, ymax=rt + ci), 
             width=.2, color = "gray26", 
             position = position_dodge(0.7))+
 theme_few()+
 # scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Subject-Wise

```{r, echo=FALSE}

library(ggplot2)
library(ggthemes)

sem_rt %>% 
  ggplot(aes(x = pathlengthfac, y = rt, 
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  guides(color = FALSE)+
 # scale_x_continuous(breaks = c(1,2,3,4,6,15))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_blank(),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

# z-scored Reaction Time

## Histogram of RT

```{r, echo=FALSE}
library(ggplot2)
library(ggthemes)
ggplot(sem, aes(x = rt))+
geom_histogram(binwidth = 200, color = "gray4", fill = "goldenrod1")+
    theme_few()+
  #facet_wrap(~subject)+
  xlab("Raw RT") + ylab("Count") + 
  ggtitle("Raw RT Histogram for All Trials")
```

## First Trim

```{r, echo=FALSE}
library(dplyr)
sem_firsttrim = sem %>% filter( rt > 250 & rt < 2000)
ggplot(sem_firsttrim, aes(x = rt))+
geom_histogram(binwidth = 50, color = "gray4", fill = "goldenrod1")+
    theme_few()+
  #facet_wrap(~subject)+
  xlab("Raw RT") + ylab("Count") + 
  ggtitle("Raw RT Histogram for Trials Above 250 ms and below 2000 ms")
```

## Raw RT aggregates After Trimming

```{r, echo=FALSE}
sem_rt_firsttrim = group_by(sem_firsttrim, subject, pathlength ) %>%
  summarise_at(vars(rt), mean)

sem_rt_agg_firsttrim = group_by(sem_firsttrim, pathlength ) %>%
  summarise_at(vars(rt), mean)

sem_rt_agg_firsttrim$pathlengthfac = ordered(as.factor(as.character(sem_rt_agg_firsttrim$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

library(ggplot2)
library(ggthemes)

sem_rt_agg_firsttrim %>% 
  ggplot(aes(x = pathlengthfac, y = rt, group = 1))+
  geom_point()+
  geom_line(color = "red")+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,6,15))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Subject Raw RT again


```{r, echo=FALSE}

library(ggplot2)
library(ggthemes)

sem_rt_firsttrim$pathlengthfac = ordered(as.factor(as.character(sem_rt_firsttrim$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
sem_rt_firsttrim$subject = as.factor(sem_rt_firsttrim$subject)
sem_rt_firsttrim %>% 
  ggplot(aes(x = pathlengthfac, y = rt,
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  guides(color = FALSE)+
#  scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Making the z-scores
```{r, echo=FALSE}
## aggregate per subject all IVs and DVs
meanRT = group_by(sem_firsttrim, subject) %>%
  summarise_at(vars(rt), mean)
colnames(meanRT) = c("subject", "MeanRT")

sdRT = group_by(sem_firsttrim, subject) %>%
  summarise_at(vars(rt), sd)
colnames(sdRT) = c("subject", "sdRT")

RT_agg = merge(meanRT, sdRT, by = "subject")

## merge aggregate info with long data
sem_z = merge(sem_firsttrim, RT_agg, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
sem_z = sem_z %>% mutate(zRT = (rt - MeanRT)/sdRT)
                 
## checking: subject level means should be zero

sub_pic = group_by(sem_z, subject) %>%
  summarise_at(vars(zRT), mean)

```
## z-RT Distribution
```{r, echo=FALSE}
ggplot(sem_z, aes(x = zRT))+
geom_histogram(binwidth = 0.5, color = "gray4", fill = "goldenrod1")+
    theme_few()+
  xlab("z RT") + ylab("Count") + 
  ggtitle("z-RT Histogram for above 250 ms & <2s Trials")
```

## Trimming z-RT

```{r, echo=FALSE}
sem_z_trimmed = subset(sem_z, sem_z$zRT < 3 & sem_z$zRT > -3)

ggplot(sem_z_trimmed, aes(x = zRT))+
geom_histogram(binwidth = 0.25, color = "gray4", fill = "goldenrod1")+
    theme_few()+
  xlab("Raw RT") + ylab("Count") + 
  ggtitle("Trimmed (3 SD) z-RT Histogram for above 250 ms & <2s Trials")
```

## Repeating z-scoring

```{r, echo=FALSE}
library(dplyr)

## aggregate per subject all IVs and DVs
meanRT_trim = group_by(sem_z_trimmed, subject) %>%
  summarise_at(vars(rt), mean)
colnames(meanRT_trim) = c("subject", "MeanRT_trim")

sdRT_trim = group_by(sem_z_trimmed, subject) %>%
  summarise_at(vars(rt), sd)
colnames(sdRT_trim) = c("subject", "sdRT_trim")

RT_agg_trim = merge(meanRT_trim, sdRT_trim, by = "subject")

## merge aggregate info with long data
new_sem_z = merge(sem_z_trimmed, RT_agg_trim, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
new_sem_z = new_sem_z %>% mutate(zRT_trim = (rt - MeanRT_trim)/sdRT_trim)
                 
## checking: subject level means should be zero

sub_pic = group_by(new_sem_z, subject) %>%
  summarise_at(vars(zRT_trim), mean)

#write.csv(new_pic_z, file="final_pic_z.csv")
```

## Aggregating zRT
```{r, echo=FALSE}
z_sem_rt = group_by(new_sem_z, subject, pathlength ) %>%
  summarise_at(vars(zRT_trim), mean)

z_sem_rt_rel = group_by(new_sem_z, subject, pathlength, Type ) %>%
  summarise_at(vars(zRT_trim), mean)

z_sem_rt_agg = group_by(new_sem_z, pathlength ) %>%
  summarise_at(vars(zRT_trim), mean)

z_rmisc = Rmisc::summarySE(new_sem_z, 
                        measurevar = "zRT_trim",
                        groupvars = c("pathlength"))

z_sem_rt_rel_agg = group_by(new_sem_z, pathlength, Type ) %>%
  summarise_at(vars(zRT_trim), mean)
```

## ANOVA
```{r}
z_sem_rt$pathlengthfac = ordered(as.factor(as.character(z_sem_rt$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
z_sem_rt$subject = as.factor(z_sem_rt$subject)

z_rt_aov = aov(data = z_sem_rt, zRT_trim ~ pathlengthfac + 
                     Error(subject/(pathlengthfac)))
summary(z_rt_aov)
```

## Plotting RTs: collapsed 

```{r, echo=FALSE}

z_rmisc$pathlengthfac = ordered(as.factor(as.character(z_rmisc$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

z_rmisc$zRT_trim = as.numeric(z_rmisc$zRT_trim)

library(ggplot2)
library(ggthemes)

z_rmisc %>% 
  ggplot(aes(x = pathlengthfac, y = zRT_trim, group = 1))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line(color = "red")+
   geom_errorbar(aes(ymin=zRT_trim - ci, ymax=zRT_trim + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT") + 
  ggtitle("z-RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Plotting RTs: Rel-Unrel 

```{r, echo=FALSE}

z_sem_rt_rel_agg$pathlengthfac = ordered(as.factor(as.character(z_sem_rt_rel_agg$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

z_sem_rt_rel_agg$zRT_trim = as.numeric(z_sem_rt_rel_agg$zRT_trim)

library(ggplot2)
library(ggthemes)

z_sem_rt_rel_agg %>% 
  ggplot(aes(x = pathlengthfac, y = zRT_trim, group = Type, color = Type))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line()+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT") + 
  ggtitle("z-RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Plotting RTs: Subject Wise Rel-Unrel 

```{r, echo=FALSE}

z_sem_rt_rel$pathlengthfac = ordered(as.factor(as.character(z_sem_rt_rel$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

z_sem_rt_rel$zRT_trim = as.numeric(z_sem_rt_rel$zRT_trim)

library(ggplot2)
library(ggthemes)

z_sem_rt_rel %>% 
  ggplot(aes(x = pathlengthfac, y = zRT_trim, color = Type, group=interaction(Type, subject))) + 
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line()+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT") + 
  ggtitle("z-RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Quadratic Trend

```{r}
z_sem_rt %>% 
  ggplot(aes(x = pathlength, y = zRT_trim))+
  geom_point(color = "black", size = 1)+
  geom_smooth(method = "loess", color = "red")+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
 # scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT") + 
  ggtitle("z-RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```


## Subject-Wise

```{r, echo=FALSE}

library(ggplot2)
library(ggthemes)

 

z_sem_rt %>% 
  ggplot(aes(x = pathlengthfac, y = zRT_trim,
             color = subject, group = subject))+
  geom_point(color = "black", size = 1)+
  geom_line()+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  guides(color = FALSE)+
 # scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT") + 
  ggtitle("z-RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

# Regressions
```{r, echo=FALSE}
library(lme4)
sem$pathlengthfac = ordered(as.factor(as.character(sem$pathlength)), 
                            levels = c("1", "2", "3", "4", "6","15"))

new_sem_z$pathlengthfac = ordered(as.factor(as.character(new_sem_z$pathlength)), 
                            levels = c("1", "2", "3", "4", "6","15"))
 
m0 = lmer(data = new_sem_z, rt ~ 1 + (1|subject) + (1|trial_index) +
            (1|prime_word) + (1|target_word))
summary(m0)
reghelper::ICC(m0)

contrasts(sem$pathlengthfac) = contr.treatment(6, base = 1)


contrasts(new_sem_z$pathlengthfac) = contr.treatment(6, base = 2)

m1_fixed = lmer(data = new_sem_z, zRT_trim ~ pathlengthfac +
           (1|subject))
summary(m1_fixed)

m1_random = lmer(data = sem, rt ~ pathlengthfac +
           (pathlengthfac|subject))
summary(m1_random)
```

## ELP Model

```{r}
## Adding ELP covariates

elp_model = lmer(data = new_sem_z, rt ~ mean_len + mean_logf +
                   mean_ldtz + 
           (1|subject) + (1|trial_index))
fit_from_elp = broom::augment(elp_model,new_sem_z)
 
contrasts(fit_from_elp$pathlengthfac) = contr.treatment(6, base = 2)
 
m1_fixed_elp = lmer(data = fit_from_elp, .resid ~ pathlengthfac +
           (1|subject) + (1|trial_index))
 summary(m1_fixed_elp)
 
 m1_all_elp = lmer(data = new_sem_z, rt ~ pathlengthfac +
                     mean_len + mean_logf + mean_ldtz + 
           (1|subject) + (1|trial_index))
 summary(m1_all_elp)
```


### Plot from ELP Model

```{r}
fixed.frame <- 
  data.frame(expand.grid( pathlengthfac = c("1","2", "3",
                                            "4", "6", "15"))) %>%
  mutate(pred = predict(m1_fixed_elp, newdata = ., re.form = NA))


fixed.frame %>% 
  mutate(Pathlength = factor(pathlengthfac, 
    levels = unique(pathlengthfac),
                    labels = c("1","2", "3",
                               "4", "6", "15")))%>%
ggplot(aes(x = Pathlength, y = pred, group = 1))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line(color = "green")+
 theme_few()+
  xlab("Path Length") + ylab("RT residuals ") + 
  ggtitle("z-RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))

```



# Concreteness Norms

```{r}
elpnorms = read.csv("ELP_norms.csv", header = TRUE, sep = ",")
elpnorms = elpnorms[,c(1,2)]
colnames(elpnorms) = c("prime_word", "prime_concreteness")
elpnorms$prime_word = toupper(elpnorms$prime_word)
elpnorms$prime_word = paste(elpnorms$prime_word, "")

elpnorms$prime_word = as.character(elpnorms$prime_word)

sem$prime_word = as.character(sem$prime_word)
merged_sem_prime= inner_join(sem, elpnorms, by = "prime_word")
merged_sem_prime = merged_sem_prime[,c(4,7,15,37)]

colnames(elpnorms) = c("target_word", "target_concreteness")
sem$target_word = as.character(sem$target_word)
merged_sem_target= inner_join(sem, elpnorms, by = "target_word")
merged_sem_target = merged_sem_target[,c(4,7, 16,37)]

merged_concretness = full_join(merged_sem_prime, merged_sem_target,
                           by = c("trial_index", "subject"))
merged_concretness$mean_conc = (merged_concretness$prime_concreteness +
                                merged_concretness$target_concreteness) / 2

### NOW WE HAVE CONCRETENESS NORMS FOR ALL ITEMS IN THE DATASET
### NEED TO COMBINE THIS WITH ACTUAL SEM DATA

new_sem_z$prime_word = as.character(new_sem_z$prime_word)
new_sem_z$target_word = as.character(new_sem_z$target_word)
final_sem = inner_join(new_sem_z, merged_concretness, 
                      by = c("trial_index", "subject", 
                             "prime_word", "target_word") )

```

### Conreteness Model

```{r}
final_sem$pathlengthfac = ordered(as.factor(as.character(final_sem$pathlength)), 
                            levels = c("1", "2", "3", "4", "6","15"))
 
elp_model = lmer(data = final_sem, zRT_trim ~ mean_len + mean_logf +
                   mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index))
fit_from_elp = broom::augment(elp_model,final_sem)
 
contrasts(fit_from_elp$pathlengthfac) = contr.treatment(6, base = 2)
 
m1_fixed_elp = lmer(data = fit_from_elp, .resid ~ pathlengthfac +
           (1|subject) + (1|trial_index))
 summary(m1_fixed_elp)
 
 contrasts(final_sem$pathlengthfac) = contr.treatment(6, base = 2)

 m1_all_elp = lme4::lmer(data = final_sem, zRT_trim ~ pathlengthfac*Type +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
 summary(m1_all_elp)
 
```
### Plot
```{r}

mean_length = mean(final_sem$mean_len, na.rm = TRUE)
mean_logfreq = mean(final_sem$mean_logf, na.rm = TRUE)
mean_lexdec = mean(final_sem$mean_ldtz, na.rm = TRUE)
mean_concreteness = mean(final_sem$mean_conc, na.rm = TRUE)


fixed.frame <- 
  data.frame(expand.grid( pathlengthfac = c("1","2", "3",
                                            "4", "6", "15"), 
                          Type= c("Related", "Unrelated"),
                          mean_len = mean_length,
                          mean_logf = mean_logfreq,
                          mean_ldtz = mean_lexdec,
                          mean_conc = mean_concreteness)) %>%
  mutate(pred = predict(m1_all_elp, newdata = ., re.form = NA))


fixed.frame %>% 
  mutate(Pathlength = factor(pathlengthfac, 
    levels = unique(pathlengthfac),
                    labels = c("1","2", "3",
                               "4", "6", "15")))%>%
ggplot(aes(x = Pathlength, y = pred, group = Type, color = Type))+
  geom_point()+
  geom_line()+
#  geom_smooth(method = "loess")+
#geom_line(color = "green")+
 theme_few()+
  xlab("Path Length") + ylab("z-scored RT") + 
  ggtitle("z-scored RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

# Quadratic Model

```{r}
## TESTING QUADRATIC TREND
m3_linear = lmer(data = final_sem, zRT_trim~ pathlength  +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
summary(m3_linear)
m3_quad = lmer(data = final_sem, zRT_trim ~ pathlength + I((pathlength)^2) +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
summary(m3_quad)

anova(m3_linear, m3_quad)
sjPlot::sjp.lm(m3_quad, type = "poly", poly.term = "pathlength")

```

# Other Networks

## Kenett Path Length

```{r}
items_kenett = group_by(final_sem, pathlength) %>%
  summarise(items = n())

items_kenett$pathlength = as.factor(items_kenett$pathlength)
ggplot(items_kenett, aes(x = pathlength, y = items))+
 geom_bar(stat = "identity", position = "dodge", width = 0.7, color= "black")+
 theme_few()+
  xlab("Kenett Path Length") + ylab("Number of Items") + 
  ggtitle("Kenett Item Distribution")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```


## Undirected
```{r}
items_undirected = group_by(final_sem, undirected) %>%
  summarise(items = n())

items_undirected_subject = group_by(final_sem, subject, undirected) %>%
  summarise(items = n())

undirected_rmisc = Rmisc::summarySE(items_undirected_subject, 
                        measurevar = "items",
                        groupvars = c("undirected"))


final_sem$undirectedfac = ordered(as.factor(as.character(final_sem$undirected)), 
                            levels = c("1", "2", "3", "4"))
contrasts(final_sem$undirectedfac) = contr.treatment(4, base = 2)

m_undirected = lmer(data = final_sem, zRT_trim~ undirectedfac*Type +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
summary(m_undirected)

```

### Plot Item Distribution

```{r}
ggplot(undirected_rmisc, aes(x = undirected, y = items))+
 geom_bar(stat = "identity", position = "dodge", width = 0.7, color= "black")+
 theme_few()+
  xlab("Non-directed Path Length") + ylab("Number of Items") + 
  ggtitle("Non-Directed Item Distribution")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Plot Undirecred
```{r}

mean_length = mean(final_sem$mean_len, na.rm = TRUE)
mean_logfreq = mean(final_sem$mean_logf, na.rm = TRUE)
mean_lexdec = mean(final_sem$mean_ldtz, na.rm = TRUE)
mean_concreteness = mean(final_sem$mean_conc, na.rm = TRUE)


fixed.frame <- 
  data.frame(expand.grid( undirectedfac = c("1", "2", "3", "4"),
                          Type = c("Related", "Unrelated"),
                          mean_len = mean_length,
                          mean_logf = mean_logfreq,
                          mean_ldtz = mean_lexdec,
                          mean_conc = mean_concreteness)) %>%
  mutate(pred = predict(m_undirected, newdata = ., re.form = NA))


fixed.frame %>% 
  mutate(Pathlength = factor(undirectedfac, 
    levels = unique(undirectedfac),
                    labels = c("1","2", "3","4")))%>%
ggplot(aes(x = Pathlength, y = pred, group = Type, color = Type))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line()+
 theme_few()+
  xlab("Path Length") + ylab("z-scored RT") + 
  ggtitle("z-scored RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Directed
```{r}



final_sem$newdirected = ifelse(final_sem$directed == "Inf" | 
                              final_sem$directed == "NA", NA,
                              final_sem$directed)

final_sem$directedcollapsed = ifelse((final_sem$newdirected == "5" |
                                      final_sem$newdirected == "6" |
                                       final_sem$newdirected == "7" |
                                       final_sem$newdirected == "8"), "H",
                              final_sem$newdirected)

items_directed = group_by(final_sem, newdirected) %>%
  summarise(items = n())

items_directed_subject = group_by(final_sem, subject, newdirected) %>%
  summarise(items = n())

directed_rmisc = Rmisc::summarySE(items_directed_subject, 
                        measurevar = "items",
                        groupvars = c("newdirected"))


final_sem$directedfac = 
  ordered(as.factor(as.character(final_sem$newdirected)), 
                            levels = c("1", "2", "3", "4", "5", 
                                       "6", "7", "8"))
contrasts(final_sem$directedfac) = contr.treatment(8, base = 2)

final_sem$collapsedfac = 
  ordered(as.factor(as.character(final_sem$directedcollapsed)), 
                            levels = c("1", "2", "3", "4", "H"))
contrasts(final_sem$collapsedfac) = contr.treatment(5, base = 2)

m_directed = lme4::lmer(data = final_sem, zRT_trim ~ collapsedfac*Type  +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
summary(m_directed)
```

### Plot Item Distribution

```{r}
items_directed$newdirected = as.factor(items_directed$newdirected)
ggplot(directed_rmisc, aes(x = newdirected, y = items))+
 geom_bar(stat = "identity", position = "dodge", width = 0.7, color= "black")+
 theme_few()+
  xlab("Directed Path Length") + ylab("Number of Items") + 
  ggtitle("Directed Item Distribution")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```
### Plot Directed
```{r}

mean_length = mean(final_sem$mean_len, na.rm = TRUE)
mean_logfreq = mean(final_sem$mean_logf, na.rm = TRUE)
mean_lexdec = mean(final_sem$mean_ldtz, na.rm = TRUE)
mean_concreteness = mean(final_sem$mean_conc, na.rm = TRUE)


fixed.frame <-
  data.frame(expand.grid( collapsedfac = c("1", "2", "3", "4", "H"),
                          Type = c("Related", "Unrelated"),
                          mean_len = mean_length,
                          mean_logf = mean_logfreq,
                          mean_ldtz = mean_lexdec,
                          mean_conc = mean_concreteness)) %>%
  mutate(pred = predict(m_directed, newdata = ., re.form = NA))

# fixed.frame <- 
#   data.frame(expand.grid( newdirected = 
#                             seq(min(final_sem$newdirected, na.rm = TRUE), 
#                                 max(final_sem$newdirected, na.rm = TRUE),
#                                 1),
#                           mean_len = mean_length,
#                           mean_logf = mean_logfreq,
#                           mean_ldtz = mean_lexdec,
#                           mean_conc = mean_concreteness)) %>%
#   mutate(pred = predict(m_directed, newdata = ., re.form = NA))


fixed.frame %>% 
 mutate(Pathlength = factor(collapsedfac,
  levels = unique(collapsedfac),
                 labels = c("1","2", "3","4", "H")))%>%
ggplot(aes(x = collapsedfac, y = pred, group = Type, color = Type))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line()+
 theme_few()+
  xlab("Path Length") + ylab("z-scored RT") + 
  ggtitle("z-scored RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```
## Log P
```{r}
final_sem$logp = round(final_sem$logp, 2)

final_sem$newlogp = ifelse(final_sem$logp == "Inf" | 
                              final_sem$logp == "NA", NA,
                              final_sem$logp)
final_sem$roundedlogp = round(final_sem$newlogp, 0)

items_logp = group_by(final_sem, roundedlogp) %>%
  summarise(items = n())

items_logp_subject = group_by(final_sem, subject, roundedlogp) %>%
  summarise(items = n())

logp_rmisc = Rmisc::summarySE(items_logp_subject, 
                        measurevar = "items",
                        groupvars = c("roundedlogp"))


m_logp = lmer(data = final_sem, zRT_trim ~ newlogp  +
                     mean_len + mean_logf + mean_ldtz + mean_conc +
           (1|subject) + (1|trial_index) +
              + (1|target_word))
summary(m_logp)
```

### Plot Item Distribution

```{r}
items_logp$roundedlogp = as.factor(items_logp$roundedlogp)
ggplot(items_logp, aes(x = roundedlogp, y = items))+
 geom_bar(stat = "identity", position = "dodge", width = 0.2, color= "black")+
 theme_few()+
  xlab("Directed Path Length") + ylab("Number of Items") + 
  ggtitle("Log P Item Distribution")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Plot LogP
```{r}

mean_length = mean(final_sem$mean_len, na.rm = TRUE)
mean_logfreq = mean(final_sem$mean_logf, na.rm = TRUE)
mean_lexdec = mean(final_sem$mean_ldtz, na.rm = TRUE)
mean_concreteness = mean(final_sem$mean_conc, na.rm = TRUE)

fixed.frame <- 
  data.frame(expand.grid( newlogp = 
                            seq(min(final_sem$newlogp, na.rm = TRUE), 
                                max(final_sem$newlogp, na.rm = TRUE),
                                2),
                          mean_len = mean_length,
                          mean_logf = mean_logfreq,
                          mean_ldtz = mean_lexdec,
                          mean_conc = mean_concreteness)) %>%
  mutate(pred = predict(m_logp, newdata = ., re.form = NA))


fixed.frame %>% 
 # mutate(Pathlength = factor(directedfac, 
  #  levels = unique(directedfac),
   #                 labels = c("1","2", "3","4", 
    #                                      "5", "6", "7", "8")))%>%
ggplot(aes(x = newlogp, y = pred, group = 1))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line(color = "green")+
 theme_few()+
  xlab("Path Length") + ylab("z-scored RT") + 
  ggtitle("z-scored RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

# z-scores for Path Lengths

```{r}
library(dplyr)
z_pathlength1 = final_sem %>% filter(pathlength == "1")
z_pathlength2 = final_sem %>% filter(pathlength == "2")
z_pathlength3 = final_sem %>% filter(pathlength == "3")
z_pathlength4 = final_sem %>% filter(pathlength == "4")
z_pathlength6 = final_sem %>% filter(pathlength == "6")
z_pathlength15 = final_sem %>% filter(pathlength == "15")

rawRT_p1 = sem %>% filter(pathlength == "1")

```

## Creating separate z-scores
```{r}

sem_firsttrim1 = sem_firsttrim %>% filter(pathlength == "15")

## aggregate per subject all IVs and DVs
meanRT = group_by(sem_firsttrim1, subject) %>%
  summarise_at(vars(rt), mean)
colnames(meanRT) = c("subject", "MeanRT")

sdRT = group_by(sem_firsttrim1, subject) %>%
  summarise_at(vars(rt), sd)
colnames(sdRT) = c("subject", "sdRT")

RT_agg = merge(meanRT, sdRT, by = "subject")

## merge aggregate info with long data
sem_z_1 = merge(sem_firsttrim1, RT_agg, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
sem_z_1 = sem_z_1 %>% mutate(zRT = (rt - MeanRT)/sdRT)
                 
## checking: subject level means should be zero

sub_pic = group_by(sem_z_1, subject) %>%
  summarise_at(vars(zRT), mean)
```



```




