---
title: "Semantic Networks"
author: "Abhilasha Kumar"
date: "December 14, 2017"
output: html_document
code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Semantic Networks Project: Reading the Data

We are not going to read all the files into R. They are in the folder. At this point, I am plotting only descriptives of number of items for each path length. 

## Kenett Network
```{r}
kenett = data.frame(PathLength = c(1,2,3,4,5,6,10,15,20, 25, 30, 35,40,
                                   45,50,55,60), 
                    WordPairs =c(29362, 87796, 159802, 247114, 349286, 440964, 
                     659580, 798116, 778900,714168, 541684,
                     502740, 311442, 190726, 140938, 39866, 76) )


library(ggplot2)
library(ggthemes)
library(dplyr)
require(scales)
kenett %>% mutate(Path = factor(PathLength, levels = unique(PathLength),
                          labels = c(1,2,3,4,5,6,10,15,20, 25, 30, 35,40,
                                   45,50,55,60)))%>%
ggplot(aes(x = Path, y = WordPairs)) +
 geom_bar(stat = "identity", position = "dodge", 
          width = 1, color = "gray4", fill = "seagreen")+
    xlab("Path Length") + ylab ("Number of Word Pairs")+ 
  ggtitle("Distribution of Word Pairs in Kenett network")+
  scale_y_continuous(labels = comma)+
theme_classic() +
    theme(axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          legend.title = element_text(face = "bold", size = rel(1.2)),
          plot.title = element_text(face = "bold", size = rel(1.2), hjust = .5))
```

## Undirected Steyvers and Tenenbaum (2005) Network

```{r}
undirected_2005 = data.frame(PathLength = c(1,2,3,4,5,6,10,15,20), 
                    WordPairs =c(110464, 3059056,17694010,4304976, 6800, 0,0,0,0))

library(ggplot2)
library(ggthemes)
library(dplyr)
require(scales)
undirected_2005 %>% mutate(Path = factor(PathLength, levels = unique(PathLength),
                          labels = c(1,2,3,4,5,6,10,15,20)))%>%
ggplot(aes(x = Path, y = WordPairs)) +
 geom_bar(stat = "identity", position = "dodge", 
          width = 1, color = "gray4", fill = "seagreen")+
    xlab("Path Length") + ylab ("Number of Word Pairs")+ 
  ggtitle("Distribution of Word Pairs in \n Undirected Steyvers & Tenenbaum")+
theme_classic() +
    scale_y_continuous(labels = comma)+
    theme(axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          legend.title = element_text(face = "bold", size = rel(1.2)),
          plot.title = element_text(face = "bold", size = rel(1.2), hjust = .5))
```

## Undirected Steyvers and Tenenbaum (2005) Network

```{r}
directed_2005 = data.frame(PathLength = c(1,2,3,4,5,6,10,15,20), 
                    WordPairs =c(63616, 634572,4018286,10090612, 
                                 7397671, 1836567,6,0,0))

library(ggplot2)
library(ggthemes)
library(dplyr)
require(scales)
directed_2005 %>% mutate(Path = factor(PathLength, levels = unique(PathLength),
                          labels = c(1,2,3,4,5,6,10,15,20)))%>%
ggplot(aes(x = Path, y = WordPairs)) +
 geom_bar(stat = "identity", position = "dodge", 
          width = 1, color = "gray4", fill = "seagreen")+
    xlab("Path Length") + ylab ("Number of Word Pairs")+ 
  ggtitle("Distribution of Word Pairs in \n Directed Step Distance Network")+
theme_classic() +
    scale_y_continuous(labels = comma)+
    theme(axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          legend.title = element_text(face = "bold", size = rel(1.2)),
          plot.title = element_text(face = "bold", size = rel(1.2), hjust = .5))
```

## Directed Log P Steyvers and Tenenbaum (2005) Network

```{r}
undirected_2005 = data.frame(PathLength = c(1,2,3,4,5,6,10,15,20, 25, 30, 35, 40), 
                    WordPairs =c(1639, 3567, 7186,13722,24540, 51544,
                                 259257,1371146,2176554, 879401, 137398, 18878,
                                 1085))

library(ggplot2)
library(ggthemes)
library(dplyr)
require(scales)
undirected_2005 %>% mutate(Path = factor(PathLength, levels = unique(PathLength),
                          labels = c(1,2,3,4,5,6,10,15,20, 25, 30,35,40)))%>%
ggplot(aes(x = Path, y = WordPairs)) +
 geom_bar(stat = "identity", position = "dodge", 
          width = 1, color = "gray4", fill = "seagreen")+
    xlab("Path Length") + ylab ("Number of Word Pairs")+ 
  ggtitle("Distribution of Word Pairs in \n Directed Log P network")+
theme_classic() +
    scale_y_continuous(labels = comma)+
    theme(axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          legend.title = element_text(face = "bold", size = rel(1.2)),
          plot.title = element_text(face = "bold", size = rel(1.2), hjust = .5))
```

# Path Length Correlations

## Sample 1

```{r}
kenett_1 = read.csv("kenett_random_1.csv", header = TRUE,sep = ",")
undirected_1 = read.csv("undirected_random_1.csv", header = TRUE,sep = ",")
directed_1 = read.csv("directed_random_1.csv", header = TRUE,sep = ",")
directedlogp_1 = read.csv("directedlogp_random_1.csv", header = TRUE,sep = ",")

sample_1 = Reduce(function(dtf1, dtf2) merge(dtf1, dtf2, 
                  by = c("X", "Word1", "Word2"), all = TRUE), 
                  list(kenett_1, undirected_1, directed_1, directedlogp_1))

library(dplyr)
sample_1 = sample_1 %>% filter(PathLengthKenett != "Inf" &
                                 PathLengthUndirected != "Inf" &
                                 PathLengthDirected != "Inf" &
                                 PathLengthLogP != "Inf")

Hmisc::rcorr(as.matrix(sample_1[,4:7]), type = "pearson")

cor.test(sample_1$PathLengthKenett, sample_1$PathLengthUndirected)
```

### Plotting Correlations

```{r}
ggplot(sample_1, aes(x = PathLengthKenett, y = PathLengthUndirected)) +
 geom_point(color = "black", size = 0.8) + 
  geom_smooth(method = "lm", color = "purple")+
    xlab("Kenett Path Length") + ylab ("Undirected Path Length")+ 
  ggtitle("Kenett:Undirected (r = 0.04)")+
theme_classic() +
    theme(axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          legend.title = element_text(face = "bold", size = rel(1.2)),
          plot.title = element_text(face = "bold", size = rel(1.2), hjust = .5))
```


## Sample 2

```{r}
kenett_2 = read.csv("kenett_random_2.csv", header = TRUE,sep = ",")
undirected_2 = read.csv("undirected_random_2.csv", header = TRUE,sep = ",")
directed_2 = read.csv("directed_random_2.csv", header = TRUE,sep = ",")
directedlogp_2 = read.csv("directedlogp_random_2.csv", header = TRUE,sep = ",")

sample_2 = Reduce(function(dtf1, dtf2) merge(dtf1, dtf2, 
                  by = c("X", "Word1", "Word2"), all = TRUE), 
                  list(kenett_2, undirected_2, directed_2, directedlogp_2))

library(dplyr)
sample_2 = sample_2 %>% filter(PathLengthKenett != "Inf" &
                                 PathLengthUndirected != "Inf" &
                                 PathLengthDirected != "Inf" &
                                 PathLengthLogP != "Inf")

Hmisc::rcorr(as.matrix(sample_2[,4:7]), type = "pearson")
#to generate random examples:
# sample_2[c(1,25,50,70,300, 900, 235, 150, 111, 5),]
```

# ELP Data

```{r, echo=FALSE}
#k1 = read.csv("kenett_1.csv", header = TRUE, sep = ",")
#x = unique(k1$Word1)
#write.csv(x, "1_word1.csv")
```


