---
title: "Network Demasking"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading the Data

``` {r warning=F, message=F}
library(dplyr)
netdemask = read.csv("Compiled_NetworksE3_final.csv", header = TRUE, sep = ",")
## filtering out incorrect target responses
netdemask = netdemask %>% filter(TargetAccuracy == 1)
```

#Raw Reaction Time

```{r}
netdemask_rt = group_by(netdemask, subject, pathlength ) %>%
  summarise_at(vars(RTRecogniseTarget), mean)

netdemask_rt_agg = Rmisc::summarySE(netdemask_rt, 
                        measurevar = "RTRecogniseTarget",
                        groupvars = c("pathlength"))
```

### ANOVA

```{r}
netdemask_rt$pathlengthfac = ordered(as.factor(as.character(netdemask_rt$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
netdemask_rt$subject = as.factor(netdemask_rt$subject)
rt_aov = aov(data = netdemask_rt, RTRecogniseTarget ~ pathlengthfac + 
                     Error(subject/(pathlengthfac)))
summary(rt_aov)
```

### Plotting RTs

``` {r  }

netdemask_rt_agg$pathlengthfac = ordered(as.factor(as.character(netdemask_rt_agg$pathlength)),                             levels = c("1", "2", "3", "4",  "6", "15"))

library(ggplot2)
library(ggthemes)

netdemask_rt_agg %>% 
  ggplot(aes(x = pathlengthfac, y = RTRecogniseTarget, group = 1))+
  geom_point()+
  geom_line(color = "red")+
   geom_errorbar(aes(ymin=RTRecogniseTarget - se, ymax=RTRecogniseTarget + se), 
             width=.2, color = "gray26", 
             position = position_dodge(0.7))+
 theme_few()+
 # scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT to Recognise Target by Path Length")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Subject-Wise

``` {r  }

library(ggplot2)
library(ggthemes)

netdemask_rt %>% 
  ggplot(aes(x = pathlengthfac, y = RTRecogniseTarget, 
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
 theme_few()+
  guides(color = FALSE)+
 # scale_x_continuous(breaks = c(1,2,3,4,6,15))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT to demask Target")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_blank(),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

# z-scored Reaction Time

## Histogram of RT

``` {r  }
library(ggplot2)
library(ggthemes)
ggplot(netdemask, aes(x = RTRecogniseTarget))+
geom_histogram(binwidth = 200, color = "gray4", fill = "goldenrod1")+
    theme_few()+
  #facet_wrap(~subject)+
  xlab("Raw RT") + ylab("Count") + 
  ggtitle("RT to recognise Target")
```

## First Trim

``` {r  }
library(dplyr)
netdemask_firsttrim = netdemask %>% filter(RTRecogniseTarget > 250 &  
                                             RTRecogniseTarget < 7000)
```

## Raw RT aggregates After Trimming

``` {r  }
netdemask_rt_firsttrim = group_by(netdemask_firsttrim, subject, pathlength ) %>%
  summarise_at(vars(RTRecogniseTarget), mean)

netdemask_rt_agg_firsttrim = group_by(netdemask_firsttrim, pathlength ) %>%
  summarise_at(vars(RTRecogniseTarget), mean)

netdemask_rt_agg_firsttrim$pathlengthfac = ordered(as.factor(as.character(netdemask_rt_agg_firsttrim$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

library(ggplot2)
library(ggthemes)

netdemask_rt_agg_firsttrim %>% 
  ggplot(aes(x = pathlengthfac, y = RTRecogniseTarget, group = 1))+
  geom_point()+
  geom_line(color = "red")+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,6,15))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Subject Raw RT again


``` {r  }

library(ggplot2)
library(ggthemes)

netdemask_rt_firsttrim$pathlengthfac = ordered(as.factor(as.character(netdemask_rt_firsttrim$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
netdemask_rt_firsttrim$subject = as.factor(netdemask_rt_firsttrim$subject)
netdemask_rt_firsttrim %>% 
  ggplot(aes(x = pathlengthfac, y = RTRecogniseTarget,
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  #guides(color = FALSE)+
#  scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Making the z-scores
``` {r  }
## aggregate per subject all IVs and DVs
meanRT = group_by(netdemask_firsttrim, subject) %>%
  summarise_at(vars(RTRecogniseTarget), mean)
colnames(meanRT) = c("subject", "MeanRTTarget")

sdRT = group_by(netdemask_firsttrim, subject) %>%
  summarise_at(vars(RTRecogniseTarget), sd)
colnames(sdRT) = c("subject", "sdRTTarget")

RT_agg = merge(meanRT, sdRT, by = "subject")

## merge aggregate info with long data
netdemask_z = merge(netdemask_firsttrim, RT_agg, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
netdemask_z = netdemask_z %>% mutate(zRTTarget = 
                            (RTRecogniseTarget - MeanRTTarget)/sdRTTarget)
                 
## checking: subject level means should be zero

sub_pic = group_by(netdemask_z, subject) %>%
  summarise_at(vars(zRTTarget), mean)

```
## z-RT Distribution
``` {r  }
ggplot(netdemask_z, aes(x = zRTTarget))+
geom_histogram(binwidth = 0.5, color = "gray4", fill = "goldenrod1")+
    theme_few()+
  xlab("z RT") + ylab("Count") + 
  ggtitle("z-RT Histogram for above 250 ms & <2s Trials")
```

## Trimming z-RT

``` {r  }
## trimming separately for prime and target
netdemask_z_trimmed_target = subset(netdemask_z, netdemask_z$zRTTarget < 3 &
                               netdemask_z$zRTTarget > -3)
```

## Repeating z-scoring

``` {r  }
library(dplyr)
## FOR TARGET
## aggregate per subject all IVs and DVs
meanRT_trim_target = group_by(netdemask_z_trimmed_target, subject) %>%
  summarise_at(vars(RTRecogniseTarget), mean)
colnames(meanRT_trim_target) = c("subject", "MeanRT_trim_target")

sdRT_trim_target = group_by(netdemask_z_trimmed_target, subject) %>%
  summarise_at(vars(RTRecogniseTarget), sd)
colnames(sdRT_trim_target) = c("subject", "sdRT_trim_target")

RT_agg_trim_target = merge(meanRT_trim_target, sdRT_trim_target, by = "subject")

## merge aggregate info with long data
new_netdemask_z_target = merge(netdemask_z_trimmed_target, 
                        RT_agg_trim_target, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
new_netdemask_z_target = new_netdemask_z_target %>% 
  mutate(zRTTarget_trim = (RTRecogniseTarget - MeanRT_trim_target)/sdRT_trim_target)
                 
## checking: subject level means should be zero

sub_pic = group_by(new_netdemask_z_target, subject) %>%
  summarise_at(vars(zRTTarget_trim), mean)


new_netdemask_z = new_netdemask_z_target

```

## Aggregating zRT
``` {r}
z_netdemask_rt = group_by(new_netdemask_z, subject, pathlength ) %>%
  summarise_at(vars(zRTTarget_trim), mean)

z_netdemask_rt_item = group_by(new_netdemask_z, ItemNumber, pathlength ) %>%
  summarise_at(vars(zRTTarget_trim), mean)

z_rmisc = Rmisc::summarySE(new_netdemask_z, 
                        measurevar = "zRTTarget_trim",
                        groupvars = c("pathlength"))
```

## Subject ANOVA
```{r}
z_netdemask_rt$pathlengthfac = ordered(as.factor(as.character(z_netdemask_rt$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
z_netdemask_rt$subject = as.factor(z_netdemask_rt$subject)

z_rt_aov = aov(data = z_netdemask_rt, zRTTarget_trim ~ pathlengthfac + 
                     Error(subject/(pathlengthfac)))
summary(z_rt_aov)

options(contrasts = c('contr.sum', 'contr.poly'))
 library(lsmeans)
 library(multcomp)
 sem_lsm = lsmeans::lsmeans(z_rt_aov, c("pathlengthfac"))
 prime_effect = cld(sem_lsm, alpha = 0.05, 
                 adjust = "tukey", details = TRUE)
 library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.1 ))

```


## Item ANOVA
```{r}
z_netdemask_rt_item$pathlengthfac = ordered(as.factor(as.character(z_netdemask_rt_item$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
z_netdemask_rt_item$ItemNumber = as.factor(z_netdemask_rt_item$ItemNumber)

z_rt_aov_item = aov(data = z_netdemask_rt_item, 
                    zRTTarget_trim ~ pathlengthfac)
summary(z_rt_aov_item)

options(contrasts = c('contr.sum', 'contr.poly'))
 library(lsmeans)
 library(multcomp)
 sem_lsm = lsmeans::lsmeans(z_rt_aov_item, c("pathlengthfac"))
 prime_effect = cld(sem_lsm, alpha = 0.05, 
                 adjust = "tukey", details = TRUE)
 library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.1 ))

```

## Plotting RTs: collapsed 

```{r}

z_rmisc$pathlengthfac = ordered(as.factor(as.character(z_rmisc$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

z_rmisc$zRTTarget_trim = as.numeric(z_rmisc$zRTTarget_trim)

library(ggplot2)
library(ggthemes)

z_rmisc %>% 
  ggplot(aes(x = pathlengthfac, y = zRTTarget_trim, group = 1))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line(color = "red")+
   geom_errorbar(aes(ymin=zRTTarget_trim - ci, ymax=zRTTarget_trim + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT to Recognise Target") + 
  ggtitle("z-RT to Demask Target by Path Length")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))

z_rmisc_kenett = z_rmisc
z_rmisc_kenett$Network = "Association Correlation"

```

## Subject z RT 


``` {r  }

library(ggplot2)
library(ggthemes)


z_netdemask_rt %>% 
  ggplot(aes(x = pathlengthfac, y = zRTTarget_trim,
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  #guides(color = FALSE)+
#  scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Quadratic Trend?

```{r}
new_netdemask_z %>%
  ggplot(aes(x = pathlength, y = zRTTarget_trim))+
 geom_point(color = "black", size = 1)+
  geom_smooth(method = "loess", color = "red")+ 
 theme_few()+
  #guides(color = FALSE)+
#  scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```


# Concreteness Norms

```{r}
elpnorms = read.csv("ELP_norms.csv", header = TRUE, sep = ",")
elpnorms = elpnorms[,c(1,2)]
colnames(elpnorms) = c("prime_word", "prime_concreteness")
elpnorms$prime_word = toupper(elpnorms$prime_word)

elpnorms$prime_word = as.character(elpnorms$prime_word)

netdemask$prime_word = as.character(netdemask$prime_word)
merged_sem_prime= inner_join(netdemask, elpnorms, by = "prime_word")
merged_sem_prime = merged_sem_prime[,c(2,5, 20,28)]

colnames(elpnorms) = c("target_word", "target_concreteness")
netdemask$target_word = as.character(netdemask$target_word)
merged_sem_target= inner_join(netdemask, elpnorms, by = "target_word")
merged_sem_target = merged_sem_target[,c(2,5, 22,28)]

merged_concretness = full_join(merged_sem_prime, merged_sem_target,
                           by = c("Trial", "subject"))
merged_concretness$mean_conc = (merged_concretness$prime_concreteness +
                                merged_concretness$target_concreteness) / 2

### NOW WE HAVE CONCRETENESS NORMS FOR ALL ITEMS IN THE DATASET
### NEED TO COMBINE THIS WITH ACTUAL SEM DATA

new_netdemask_z$prime_word = as.character(new_netdemask_z$prime_word)
new_netdemask_z$target_word = as.character(new_netdemask_z$target_word)
final_netdemask_z = inner_join(new_netdemask_z, merged_concretness, 
                      by = c("Trial", "subject", 
                             "prime_word", "target_word") )
```

## Model
```{r}

final_netdemask_z$mean_conc_c = scale(final_netdemask_z$mean_conc, 
                                      center = TRUE, scale = FALSE)
final_netdemask_z$mean_conc_c = as.numeric(final_netdemask_z$mean_conc_c)

final_netdemask_z$mean_len_c = scale(final_netdemask_z$MeanLength, 
                             center = TRUE, scale = FALSE)
final_netdemask_z$mean_logf_c = scale(final_netdemask_z$MeanLogF, 
                              center = TRUE, scale = FALSE)
final_netdemask_z$mean_ldtz_c = scale(final_netdemask_z$MeanLDTZ, 
                              center = TRUE, scale = FALSE)

final_netdemask_z$mean_len_c = as.numeric(final_netdemask_z$mean_len_c)
final_netdemask_z$mean_logf_c = as.numeric(final_netdemask_z$mean_logf_c)
final_netdemask_z$mean_ldtz_c = as.numeric(final_netdemask_z$mean_ldtz_c)

library(lme4)
final_netdemask_z$pathlengthfac = ordered(as.factor(as.character(final_netdemask_z$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

contrasts(final_netdemask_z$pathlengthfac) = contr.treatment(6, base = 3)
  

RTprime_model = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~ pathlengthfac + 
                         mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))
summary(RTprime_model)
car::Anova(RTprime_model)

```

# Quadratic Model

```{r}
RTprime_model_linear = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~  pathlength + 
                         mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))
summary(RTprime_model_linear)
car::Anova(RTprime_model_linear)

final_netdemask_z$pquad = (final_netdemask_z$pathlength)^2

RTprime_model_quad = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~ pathlength +
                            pquad +
                         mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))
summary(RTprime_model_quad)
car::Anova(RTprime_model_quad)

anova(RTprime_model_linear, RTprime_model_quad)
```


# Other Networks

## Steyvers Non Directed

```{r}
library(lme4)
final_netdemask_z$Undirected = as.double(as.character(final_netdemask_z$Undirected))
final_netdemask_z$Directed = as.double(as.character(final_netdemask_z$Directed))

final_netdemask_z$undirectedfac = ordered(as.factor(as.character(final_netdemask_z$Undirected)),                             levels = c("1", "2", "3", "4"))


contrasts(final_netdemask_z$undirectedfac) = contr.treatment(4, base = 3)
RTprime_undirected = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~ undirectedfac + 
                            mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))
summary(RTprime_undirected)
car::Anova(RTprime_undirected)

RTprime_undirected_linear = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~ Undirected + 
                             mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))

RTprime_undirected_quad = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~ Undirected + 
                            I(Undirected^2)+
                             mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))
summary(RTprime_undirected_quad)
car::Anova(RTprime_undirected_quad)
anova(RTprime_undirected_linear, RTprime_undirected_quad)
```

### Plot

```{r}
z_rmisc_undirected = Rmisc::summarySE(final_netdemask_z, 
                        measurevar = "zRTTarget_trim",
                        groupvars = c("Undirected"))
z_rmisc_undirected = z_rmisc_undirected %>% filter(Undirected != "NA")
z_rmisc_undirected$undirectedfac = ordered(as.factor(as.character(z_rmisc_undirected$Undirected)),                             levels = c("1", "2", "3", "4"))

z_rmisc_undirected$zRTTarget_trim = as.numeric(z_rmisc_undirected$zRTTarget_trim)

library(ggplot2)
library(ggthemes)

z_rmisc_undirected %>% 
  ggplot(aes(x = undirectedfac, y = zRTTarget_trim, group = 1))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line(color = "red")+
   geom_errorbar(aes(ymin=zRTTarget_trim - ci, ymax=zRTTarget_trim + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT to Recognise Target") + 
  ggtitle("z-RT to Demask Target by Path Length (non directed)")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))

z_rmisc_undirected$Network = "Undirected Simple Association"

```

## Steyvers Directed

```{r}
library(lme4)
final_netdemask_z$newdirected = ifelse(final_netdemask_z$Directed == "Inf" | 
                              final_netdemask_z$Directed == "NA", NA,
                              final_netdemask_z$Directed)

final_netdemask_z$directedcollapsed = ifelse((final_netdemask_z$newdirected == "6" |final_netdemask_z$newdirected == "7" | final_netdemask_z$newdirected == "8"), "H",final_netdemask_z$newdirected)


final_netdemask_z$directedfac = 
  ordered(as.factor(as.character(final_netdemask_z$newdirected)), 
                            levels = c("1", "2", "3", "4", "5", 
                                       "6", "7", "8"))
contrasts(final_netdemask_z$directedfac) = contr.treatment(8, base = 5)

final_netdemask_z$collapsedfac = 
  ordered(as.factor(as.character(final_netdemask_z$directedcollapsed)), 
                            levels = c("1", "2", "3", "4","5", "H"))
contrasts(final_netdemask_z$collapsedfac) = contr.treatment(6, base = 5)


RTprime_directed = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~ collapsedfac + 
                          mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))
summary(RTprime_directed)
car::Anova(RTprime_directed)

RTprime_directed_linear = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~ newdirected + 
                             mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))

RTprime_directed_quad = lmer(data = final_netdemask_z, 
                          zRTTarget_trim ~ newdirected + 
                            I(newdirected^2)+
                             mean_len_c + mean_logf_c + mean_ldtz_c +
                           mean_conc_c +
                            (1|subject) + (1|ItemNumber))
summary(RTprime_directed_quad)
car::Anova(RTprime_directed_quad)
anova(RTprime_directed_linear, RTprime_directed_quad)

```

### Plot Collapsed

```{r}
z_rmisc_directed = Rmisc::summarySE(final_netdemask_z, 
                        measurevar = "zRTTarget_trim",
                        groupvars = c("collapsedfac"))
z_rmisc_directed = z_rmisc_directed %>% filter(collapsedfac != "NA")
z_rmisc_directed$collapsedfac2 = ordered(as.factor(as.character(z_rmisc_directed$collapsedfac)),                             levels = c("1", "2", "3", "4", "5", "H"))

z_rmisc_directed$zRTTarget_trim = as.numeric(z_rmisc_directed$zRTTarget_trim)

z_rmisc_directed_collapsed = z_rmisc_directed

library(ggplot2)
library(ggthemes)

z_rmisc_directed_collapsed %>% 
  ggplot(aes(x = collapsedfac2, y = zRTTarget_trim, group = 1))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line(color = "red")+
   geom_errorbar(aes(ymin=zRTTarget_trim - ci, ymax=zRTTarget_trim + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT to Recognise Target") + 
  ggtitle("z-RT to Demask Target by Path Length (directed)")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))

z_rmisc_directed_collapsed$Network = "Directed Simple Association"

```

### Plot Not Collapsed

```{r}
z_rmisc_directed = Rmisc::summarySE(new_netdemask_z, 
                        measurevar = "zRTTarget_trim",
                        groupvars = c("directedfac"))
z_rmisc_directed = z_rmisc_directed %>% filter(directedfac != "NA")
z_rmisc_directed$collapsedfac2 = ordered(as.factor(as.character(z_rmisc_directed$directedfac)),                             levels = c("1", "2", "3", "4", "5", "6", "7", "8"))

z_rmisc_directed$zRTTarget_trim = as.numeric(z_rmisc_directed$zRTTarget_trim)

library(ggplot2)
library(ggthemes)

z_rmisc_directed %>% 
  ggplot(aes(x = collapsedfac2, y = zRTTarget_trim, group = 1))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line(color = "red")+
   geom_errorbar(aes(ymin=zRTTarget_trim - ci, ymax=zRTTarget_trim + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT to Recognise Target") + 
  ggtitle("z-RT to Demask Target by Path Length (directed)")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Combined Plot

```{r}
colnames(z_rmisc_directed_collapsed) = colnames(z_rmisc_kenett)
colnames(z_rmisc_undirected) = colnames(z_rmisc_kenett)
z_rmisc_directed_collapsed = z_rmisc_directed_collapsed %>%
  filter(!pathlengthfac == "H")

z_rmisc_combined = rbind(z_rmisc_kenett, z_rmisc_undirected,
                         z_rmisc_directed_collapsed)


z_rmisc_combined$Network = as.factor(z_rmisc_combined$Network)

z_rmisc_combined$pathlengthfac = ordered(as.factor(as.character(z_rmisc_combined$pathlength)), 
                            levels = c("1", "2", "3", "4", "5", "6","15"))
library(ggplot2)
library(ggthemes)

z_rmisc_combined %>% 
  ggplot(aes(x = pathlengthfac, y = zRTTarget_trim, 
             group = Network, color = Network))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line()+
   geom_errorbar(aes(ymin=zRTTarget_trim - ci, ymax=zRTTarget_trim + ci), 
             width=.05, color = "azure3", 
             position = position_dodge(0))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Network Path Length") + ylab("Standardized RT to Identify Target") + 
  ggtitle("Response Time to Demask Target by Path Length")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))

```




