---
title: "Network Demasking"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading the Data

``` {r warning=F, message=F}
library(dplyr)
netdemask = read.csv("Compiled_NetworksDemasking.csv", header = TRUE, sep = ",")
```

#Raw Reaction Time

```{r}
netdemask_rt = group_by(netdemask, subject, pathlength ) %>%
  summarise_at(vars(RTRecognisePrime, RTRecogniseTarget), mean)

netdemask_rt_agg = Rmisc::summarySE(netdemask_rt, 
                        measurevar = "RTRecogniseTarget",
                        groupvars = c("pathlength"))
```

### ANOVA

```{r}
netdemask_rt$pathlengthfac = ordered(as.factor(as.character(netdemask_rt$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
netdemask_rt$subject = as.factor(netdemask_rt$subject)
rt_aov = aov(data = netdemask_rt, RTRecogniseTarget ~ pathlengthfac + 
                     Error(subject/(pathlengthfac)))
summary(rt_aov)
```

### Plotting RTs

``` {r  }

netdemask_rt_agg$pathlengthfac = ordered(as.factor(as.character(netdemask_rt_agg$pathlength)),                             levels = c("1", "2", "3", "4",  "6", "15"))

library(ggplot2)
library(ggthemes)

netdemask_rt_agg %>% 
  ggplot(aes(x = pathlengthfac, y = RTRecogniseTarget, group = 1))+
  geom_point()+
  geom_line(color = "red")+
   geom_errorbar(aes(ymin=RTRecogniseTarget - se, ymax=RTRecogniseTarget + se), 
             width=.2, color = "gray26", 
             position = position_dodge(0.7))+
 theme_few()+
 # scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT to Recognise Target by Path Length")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

### Subject-Wise

``` {r  }

library(ggplot2)
library(ggthemes)

netdemask_rt %>% 
  ggplot(aes(x = pathlengthfac, y = RTRecogniseTarget, 
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
 theme_few()+
  guides(color = FALSE)+
 # scale_x_continuous(breaks = c(1,2,3,4,6,15))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT to demask Target")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_blank(),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

# z-scored Reaction Time

## Histogram of RT

``` {r  }
library(ggplot2)
library(ggthemes)
ggplot(netdemask, aes(x = RTRecogniseTarget))+
geom_histogram(binwidth = 200, color = "gray4", fill = "goldenrod1")+
    theme_few()+
  #facet_wrap(~subject)+
  xlab("Raw RT") + ylab("Count") + 
  ggtitle("RT to recognise Target")
```

## First Trim

``` {r  }
library(dplyr)
netdemask_firsttrim = netdemask
```

## Raw RT aggregates After Trimming

``` {r  }
netdemask_rt_firsttrim = group_by(netdemask_firsttrim, subject, pathlength ) %>%
  summarise_at(vars(RTRecognisePrime,RTRecogniseTarget), mean)

netdemask_rt_agg_firsttrim = group_by(netdemask_firsttrim, pathlength ) %>%
  summarise_at(vars(RTRecognisePrime,RTRecogniseTarget), mean)

netdemask_rt_agg_firsttrim$pathlengthfac = ordered(as.factor(as.character(netdemask_rt_agg_firsttrim$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

library(ggplot2)
library(ggthemes)

netdemask_rt_agg_firsttrim %>% 
  ggplot(aes(x = pathlengthfac, y = RTRecogniseTarget, group = 1))+
  geom_point()+
  geom_line(color = "red")+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,6,15))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Subject Raw RT again


``` {r  }

library(ggplot2)
library(ggthemes)

netdemask_rt_firsttrim$pathlengthfac = ordered(as.factor(as.character(netdemask_rt_firsttrim$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
netdemask_rt_firsttrim$subject = as.factor(netdemask_rt_firsttrim$subject)
netdemask_rt_firsttrim %>% 
  ggplot(aes(x = pathlengthfac, y = RTRecogniseTarget,
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  #guides(color = FALSE)+
#  scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Making the z-scores
``` {r  }
## aggregate per subject all IVs and DVs
meanRT = group_by(netdemask_firsttrim, subject) %>%
  summarise_at(vars(RTRecognisePrime,RTRecogniseTarget), mean)
colnames(meanRT) = c("subject", "MeanRTPrime", "MeanRTTarget")

sdRT = group_by(netdemask_firsttrim, subject) %>%
  summarise_at(vars(RTRecognisePrime,RTRecogniseTarget), sd)
colnames(sdRT) = c("subject", "sdRTPrime", "sdRTTarget")

RT_agg = merge(meanRT, sdRT, by = "subject")

## merge aggregate info with long data
netdemask_z = merge(netdemask_firsttrim, RT_agg, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
netdemask_z = netdemask_z %>% mutate(zRTTarget = 
                            (RTRecogniseTarget - MeanRTTarget)/sdRTTarget,
                        zRTPrime =  (RTRecognisePrime - MeanRTPrime)/sdRTPrime)
                 
## checking: subject level means should be zero

sub_pic = group_by(netdemask_z, subject) %>%
  summarise_at(vars(zRTTarget, zRTPrime), mean)

```
## z-RT Distribution
``` {r  }
ggplot(netdemask_z, aes(x = zRTPrime))+
geom_histogram(binwidth = 0.5, color = "gray4", fill = "goldenrod1")+
    theme_few()+
  xlab("z RT") + ylab("Count") + 
  ggtitle("z-RT Histogram for above 250 ms & <2s Trials")
```

## Trimming z-RT

``` {r  }
## trimming separately for prime and target
netdemask_z_trimmed_target = subset(netdemask_z, netdemask_z$zRTTarget < 3 &
                               netdemask_z$zRTTarget > -3)

netdemask_z_trimmed_prime = subset(netdemask_z, netdemask_z$zRTPrime < 3 &
                               netdemask_z$zRTPrime > -3)
```

## Repeating z-scoring

``` {r  }
library(dplyr)
## FOR TARGET
## aggregate per subject all IVs and DVs
meanRT_trim_target = group_by(netdemask_z_trimmed_target, subject) %>%
  summarise_at(vars(RTRecogniseTarget), mean)
colnames(meanRT_trim_target) = c("subject", "MeanRT_trim_target")

sdRT_trim_target = group_by(netdemask_z_trimmed_target, subject) %>%
  summarise_at(vars(RTRecogniseTarget), sd)
colnames(sdRT_trim_target) = c("subject", "sdRT_trim_target")

RT_agg_trim_target = merge(meanRT_trim_target, sdRT_trim_target, by = "subject")

## merge aggregate info with long data
new_netdemask_z_target = merge(netdemask_z_trimmed_target, 
                        RT_agg_trim_target, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
new_netdemask_z_target = new_netdemask_z_target %>% 
  mutate(zRTTarget_trim = (RTRecogniseTarget - MeanRT_trim_target)/sdRT_trim_target)
                 
## checking: subject level means should be zero

sub_pic = group_by(new_netdemask_z_target, subject) %>%
  summarise_at(vars(zRTTarget_trim), mean)

## FOR PRIME


meanRT_trim_prime = group_by(netdemask_z_trimmed_prime, subject) %>%
  summarise_at(vars(RTRecognisePrime), mean)
colnames(meanRT_trim_prime) = c("subject", "MeanRT_trim_prime")

sdRT_trim_prime = group_by(netdemask_z_trimmed_prime, subject) %>%
  summarise_at(vars(RTRecognisePrime), sd)
colnames(sdRT_trim_prime) = c("subject", "sdRT_trim_prime")

RT_agg_trim_prime = merge(meanRT_trim_prime, sdRT_trim_prime, by = "subject")

## merge aggregate info with long data
new_netdemask_z_prime = merge(netdemask_z_trimmed_prime, 
                        RT_agg_trim_prime, by = "subject", all.x = T)

## person and grand-mean centered scores using original and aggregate
library(dplyr)
new_netdemask_z_prime = new_netdemask_z_prime %>% 
  mutate(zRTPrime_trim = (RTRecognisePrime - MeanRT_trim_prime)/sdRT_trim_prime)
                 
## checking: subject level means should be zero

sub_pic = group_by(new_netdemask_z_prime, subject) %>%
  summarise_at(vars(zRTPrime_trim), mean)

## now we have separately z-scored RTprime and RTtarget. Need to combine.
## taking only necessary columns
new_netdemask_z_prime = new_netdemask_z_prime[,c(1,5,40)]

new_netdemask_z = merge(new_netdemask_z_target, 
                             new_netdemask_z_prime, 
                             by  = c("subject", "Trial"))

```

## Aggregating zRT
``` {r}
z_netdemask_rt = group_by(new_netdemask_z, subject, pathlength ) %>%
  summarise_at(vars(zRTTarget_trim, zRTPrime_trim), mean)

z_rmisc = Rmisc::summarySE(new_netdemask_z, 
                        measurevar = "zRTTarget_trim",
                        groupvars = c("pathlength"))
```

## ANOVA
```{r}
z_netdemask_rt$pathlengthfac = ordered(as.factor(as.character(z_netdemask_rt$pathlength)), 
                            levels = c("1", "2", "3", "4", "6", "15"))
z_netdemask_rt$subject = as.factor(z_netdemask_rt$subject)

z_rt_aov = aov(data = z_netdemask_rt, zRTTarget_trim ~ pathlengthfac + 
                     Error(subject/(pathlengthfac)))
summary(z_rt_aov)

options(contrasts = c('contr.sum', 'contr.poly'))
 library(lsmeans)
 library(multcomp)
 sem_lsm = lsmeans::lsmeans(z_rt_aov, c("pathlengthfac"))
 prime_effect = cld(sem_lsm, alpha = 0.05, 
                 adjust = "tukey", details = TRUE)
 library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.1 ))

```

## Plotting RTs: collapsed 

```{r}

z_rmisc$pathlengthfac = ordered(as.factor(as.character(z_rmisc$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))

z_rmisc$zRTTarget_trim = as.numeric(z_rmisc$zRTTarget_trim)

library(ggplot2)
library(ggthemes)

z_rmisc %>% 
  ggplot(aes(x = pathlengthfac, y = zRTTarget_trim, group = 1))+
  geom_point()+
#  geom_smooth(method = "loess")+
geom_line(color = "red")+
   geom_errorbar(aes(ymin=zRTTarget_trim - ci, ymax=zRTTarget_trim + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0.7))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT to Recognise Target") + 
  ggtitle("z-RT to Demask Target by Path Length")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

## Subject z RT 


``` {r  }

library(ggplot2)
library(ggthemes)


z_netdemask_rt %>% 
  ggplot(aes(x = pathlengthfac, y = zRTTarget_trim,
             group = subject, color = subject))+
  geom_point()+
  geom_line()+
   #geom_errorbar(aes(ymin=Trials - ci, ymax=Trials + ci), 
  #           width=.2, color = "gray26", 
   #          position = position_dodge(0.7))+
 theme_few()+
  #guides(color = FALSE)+
#  scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("Reaction Time") + 
  ggtitle("RT for Relatedness Judgments")  +
 # facet_wrap(~subject)+
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```


# Effect of Prime on Target

## Simple Scatter Plot

```{r}
ggplot(netdemask, aes(x = RTRecognisePrime, y = RTRecogniseTarget))+
geom_point()+
  geom_smooth(method = "lm", aes(group = factor(pathlength), 
                                 color = factor(pathlength)), se = FALSE)+
  theme_few()+
  #facet_wrap(~subject)+
  xlab("Raw RT") + ylab("Count") + 
  ggtitle("Raw RT Histogram for All Trials")
```

## Linear Models

```{r}
library(lme4)
new_netdemask_z$pathlengthfac = ordered(as.factor(as.character(new_netdemask_z$pathlength)),                             levels = c("1", "2", "3", "4", "6", "15"))


RTprime_model = lmer(data = new_netdemask_z, 
                          zRTTarget_trim ~ zRTPrime_trim + 
                            (1|subject) + (1|ItemNumber))
summary(RTprime_model)

contrasts(new_netdemask_z$pathlengthfac) = contr.treatment(6, base = 3)
RTprime_model_2 = lmer(data = new_netdemask_z, 
                          zRTTarget_trim ~ zRTPrime_trim*pathlengthfac + 
                            (1|subject) + (1|ItemNumber))
summary(RTprime_model_2)
car::Anova(RTprime_model_2)

options(contrasts = c('contr.sum', 'contr.poly'))
 library(lsmeans)
 library(multcomp)
 demasking_lsm = lsmeans::lsmeans(RTprime_model_2, c("zRTPrime_trim",
                                                  "pathlengthfac" ))
 prime_effect = cld(demasking_lsm, alpha = 0.05, 
                 adjust = "tukey", details = TRUE)
 library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.1 ))


RTprime_model_3 = lmer(data = new_netdemask_z, 
                          zRTTarget_trim ~ pathlengthfac + 
                            (1|subject) + (1|ItemNumber))
summary(RTprime_model_3)
car::Anova(RTprime_model_3)

anova(RTprime_model_3, RTprime_model_2)
```
## Plot
```{r}
primeplot = new_netdemask_z %>%
  ggplot(aes(x = zRTPrime_trim, y = zRTTarget_trim, 
             group = factor(subject))) +
  geom_smooth(method = "lm", se = FALSE, color = "forestgreen", size = 0.5)+
    xlab("z-RT to Demask Prime") + ylab ("z-RT to Demask Target")+ 
  ggtitle("Target Retrieval Accuracy by \nPrime Demasking RT & Prime Condition")+
theme_hc() +
  facet_wrap(~pathlengthfac)+
    theme(axis.text = element_text(face = "bold", size = rel(1.2)),
          axis.title = element_text(face = "bold", size = rel(1.2)),
          legend.title = element_text(face = "bold", size = rel(1.2)),
                   strip.text.x = element_text(face = "bold", size = rel(1.4)),
          plot.title = element_text(face = "bold", size = rel(1.2), hjust = .5))

primeplot + stat_smooth(aes(group = pathlengthfac, color = "red"), method = "lm", se = FALSE)

```
## Main effects

```{r}
new_netdemask_z %>% 
  ggplot(aes(x = zRTPrime_trim, y = zRTTarget_trim))+
#  geom_smooth(method = "loess")+
  geom_smooth(size = 1, color = "blue", method = "lm")+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("RT to recognize Prime") + ylab("RT to Recognise Target") + 
  ggtitle("Pure Demasking RT")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```

```{r}
path_group = Rmisc::summarySE(new_netdemask_z, 
                        measurevar = "zRTTarget_trim",
                        groupvars = c("pathlengthfac"))

path_group %>% 
  ggplot(aes(x = pathlengthfac, y = zRTTarget_trim))+
#  geom_smooth(method = "loess")+
  geom_bar(stat = "identity", position = "dodge", width = 0.5,
           color = "black", fill = "darkslategray4")+   
  geom_errorbar(aes(ymin=zRTTarget_trim - ci, 
                    ymax=zRTTarget_trim + ci), 
             width=.05, color = "gray30", 
             position = position_dodge(0))+
 theme_few()+
  #scale_x_continuous(breaks = c(1,2,3,4,5,6,10,15,20))+
    xlab("Path Length") + ylab("z-RT to recognise Target") + 
  ggtitle("RT to Demask Target by Path Length")  +
   theme(axis.text = element_text(size = rel(1)),
          axis.title = element_text(face = "bold", size = rel(1)),
          legend.title = element_text(face = "bold", size = rel(1)),
         plot.title = element_text(hjust = .5),
         strip.text.x = element_text(face = "bold", size = rel(1.4)))
```




